---
title: "about-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{about-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(fig.align = "center", 
               out.width = "90%",
               fig.width = 6, fig.height = 5.5)
```



```{r  message=FALSE, warning=FALSE, echo=FALSE}
library(dstats)
library(tidyverse)
library(ggplot2)
library(plotly)
```

</br></br>
## This package is written as a part of Workflows course  DSFB for educational purposes. 

<p> This RMD file contains information about the package functions that were used during this course </p>
</br></br>

####  Function dosisresponse()
</br></br>
<p> This function creates a plot with a dose response curves for given components </p> 
<p> Components: 2,6-diisopropylnaphthalene","S-medium","naphthalene", "decane"  </p>
<p> The function takes as parameter a dataset and a list of chmikals to be analysed </p>

</br></br>

```{r message=FALSE, warning=FALSE}



df <- data.frame(celegance)

components <-c("2,6-diisopropylnaphthalene","S-medium","naphthalene", "decane")

dosisresponse(df,components)


```
</br></br>
</br></br>
####  Function basestats()

</br>

</br>
<p> This functions displays base summary of given data set, and a plot of raw data density  </p>
<p> The function takes as parameter a dataset  </p>


</br></br>

### General summary of data:

</br></br>
```{r message=FALSE, warning=FALSE}
basestats(df)
```

